Simulation Study from Cheng et al. (2022)

### 2024-02-14 src/paper_sims/cheng2022handling.qmd
Updated simulation to correct problems with implementation. I think that the basic IPW and regression estimators are correct.

B <- 10
n_obs <- 2000

@@

  # 1. Estimate O00, O10, O01, O11
  df_00 <- mutate(df, A = !is.na(Y3))
  mod00 <- glm(A ~ 1, data = df_00, family = "binomial")
  O00_00 <- predict(mod00, filter(df, !is.na(Y3), is.na(Y1), is.na(Y2)))
  O00_10 <- predict(mod00, filter(df, !is.na(Y3), !is.na(Y1), is.na(Y2)))
  O00_01 <- predict(mod00, filter(df, !is.na(Y3), is.na(Y1), !is.na(Y2)))
  O00_11 <- predict(mod00, filter(df, !is.na(Y3), !is.na(Y1), !is.na(Y2)))

  df_10 <- 
    filter(df, !is.na(Y1)) |>
    mutate(A = !is.na(Y3))
  mod10 <- glm(A ~ Y1, data = df_10, family = "binomial")
  O10_10 <- predict(mod10, filter(df, !is.na(Y3), !is.na(Y1), is.na(Y2)))
  O10_11 <- predict(mod10, filter(df, !is.na(Y3), !is.na(Y1), !is.na(Y2)))

  df_01 <- 
    filter(df, !is.na(Y2)) |>
    mutate(A = !is.na(Y3))
  mod01 <- glm(A ~ Y2, data = df_01, family = "binomial")
  O01_01 <- predict(mod01, filter(df, !is.na(Y3), is.na(Y1), !is.na(Y2)))
  O01_11 <- predict(mod01, filter(df, !is.na(Y3), !is.na(Y1), !is.na(Y2)))

  df_11 <- 
    filter(df, !is.na(Y1), !is.na(Y2)) |>
    mutate(A = !is.na(Y3))
  mod11 <- glm(A ~ Y1 + Y2, data = df_11, family = "binomial")
  O11 <- predict(mod11, filter(df, !is.na(Y3), !is.na(Y1), !is.na(Y2)))

@@

  # 1. Estimate m00, m10, m01, m11
  df_00 <- filter(df, !is.na(Y3))
  m00 <- mean(df_00$Y3)

  df_10 <- filter(df, !is.na(Y3), !is.na(Y1))
  mod10 <- lm(Y3 ~ Y1, data = df_10)
  m10 <- predict(mod10, data = filter(df, is.na(Y3), !is.na(Y1)))

  df_01 <- filter(df, !is.na(Y3), !is.na(Y2))
  mod01 <- lm(Y3 ~ Y2, data = df_01)
  m01 <- predict(mod01, data = filter(df, is.na(Y3), !is.na(Y2)))

  df_11 <- filter(df, !is.na(Y3), !is.na(Y1), !is.na(Y2))
  mod01 <- lm(Y3 ~ Y1 + Y2, data = df_11)
  m11 <- predict(mod11, data = filter(df, is.na(Y3), !is.na(Y1), !is.na(Y2)))

@@

  return(sum(obs_y3 + m00 + m10 + m01 + m11) / n_tot)
}

@@

>>>>

B <- 1000
n_obs <- 2000

@@

  # 1. Estimate O00, O10, O01, O11
  df_00 <- df |>
    filter(!is.na(Y3)) |>
    add_row(Y3 = rep(NA, 250), Y1 = rep(NA, 250), Y2 = rep(NA, 250)) |>
    mutate(A = !is.na(Y3)) 
  mod00 <- glm(A ~ 1, data = df_00, family = "binomial")
  O00_00 <- exp(-predict(mod00, filter(df, !is.na(Y3), is.na(Y1), is.na(Y2))))
  O00_10 <- exp(-predict(mod00, filter(df, !is.na(Y3), !is.na(Y1), is.na(Y2))))
  O00_01 <- exp(-predict(mod00, filter(df, !is.na(Y3), is.na(Y1), !is.na(Y2))))
  O00_11 <- exp(-predict(mod00, filter(df, !is.na(Y3), !is.na(Y1), !is.na(Y2))))

  df_10 <- 
    filter(df, (!is.na(Y1) & !is.na(Y3)) | (is.na(Y3) & !is.na(Y1) & is.na(Y2))) |>
    mutate(A = !is.na(Y3))
  mod10 <- glm(A ~ Y1, data = df_10, family = "binomial")
  O10_10 <- exp(-predict(mod10, filter(df, !is.na(Y3), !is.na(Y1), is.na(Y2))))
  O10_11 <- exp(-predict(mod10, filter(df, !is.na(Y3), !is.na(Y1), !is.na(Y2))))

  df_01 <- 
    filter(df, (!is.na(Y2) & !is.na(Y3)) | (is.na(Y3) & is.na(Y1) & !is.na(Y2))) |>
    mutate(A = !is.na(Y3))
  mod01 <- glm(A ~ Y2, data = df_01, family = "binomial")
  O01_01 <- exp(-predict(mod01, filter(df, !is.na(Y3), is.na(Y1), !is.na(Y2))))
  O01_11 <- exp(-predict(mod01, filter(df, !is.na(Y3), !is.na(Y1), !is.na(Y2))))

  df_11 <- 
    filter(df, !is.na(Y1), !is.na(Y2)) |>
    mutate(A = !is.na(Y3))
  mod11 <- glm(A ~ Y1 + Y2, data = df_11, family = "binomial")
  O11 <- exp(-predict(mod11, filter(df, !is.na(Y3), !is.na(Y1), !is.na(Y2))))

@@

  # 1. Estimate m00, m10, m01, m11
  df_00 <- filter(df, !is.na(Y3))
  mod00 <- mean(df_00$Y3)
  m00 <- mod00 * rep(1, n_tot / 8)

  df_10 <- filter(df, !is.na(Y3), !is.na(Y1))
  mod10 <- lm(Y3 ~ Y1, data = df_10)
  m10 <- predict(mod10, newdata = filter(df, is.na(Y3), !is.na(Y1), is.na(Y2)))

  df_01 <- filter(df, !is.na(Y3), !is.na(Y2))
  mod01 <- lm(Y3 ~ Y2, data = df_01)
  m01 <- predict(mod01, newdata = filter(df, is.na(Y3), is.na(Y1), !is.na(Y2)))

  df_11 <- filter(df, !is.na(Y3), !is.na(Y1), !is.na(Y2))
  mod11 <- lm(Y3 ~ Y1 + Y2, data = df_11)
  m11 <- predict(mod11, newdata = filter(df, is.na(Y3), !is.na(Y1), !is.na(Y2)))

@@

  return((sum(obs_y3) + sum(m00) + sum(m10) + sum(m01) + sum(m11)) / n_tot)
}

@@

# Discussion

* While I think that I implemented this correctly, the biggest problem with this
  paper is the fact that their ACCMV assumption is almost equivalent to a MCAR
  assumption.
